Modular Model-Checking for Fault-Tolerant Distributed System Implementations

### 2016-12-06 doc/om-paper/paper.tex
Update the experiments table with results for mid-value select
Add description of mid-value select variant

\begin{figure}
  \centering
  \begin{tabular}{|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|}
  \hline
                                  & Transition systems (7 total)  &Definitions\linebreak (58 total) & Invariants\linebreak (11 total) & Invariant classes (5 total) \\
  \hline \hline
  Omissive-asymetric faults       & None                & 4 modified & 2 modified & faults             \\
  \hline
  Time-triggered messaging        & source, relays, receivers & 3 new      & 2 new, 3 modified & calendar, faults \\
  \hline
  Mid-value selection             &\lee{todo}           &  \lee{todo}&\lee{todo}  & \lee{todo}        \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications, measured by which portions of the model have to be modified.}
  \label{fig:effort}
\end{figure}

\lee{Ben: add fault-model removed plus mid-value selection models}

@@

\paragraph{Omissive asymetric faults.}
Removing faults already described by the fault model is easy. Recall that in our model faults do not appear in the system specification and only operate on the calendar. Removing a fault from the system requires only setting the number of a particular kind of faults to zero in the maximum fault assumption.

@@

\paragraph{Mid-value selection.}

\lee{todo}

\lee{any other modifications?}

>>>>

\begin{figure}
  \centering
  \begin{tabular}{|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|}
  \hline
                                  & Transition systems (7 total)  &Definitions\linebreak (58 total) & Invariants\linebreak (11 total) & Invariant classes (5 total) \\
  \hline \hline
  No Fault Model                  & receivers & 8 modified & 2 modified & ASM, faults \\
  \hline
  Omissive-asymetric faults       & None      & 4 modified & 2 modified & faults             \\
  \hline
  Time-triggered messaging        & source, relays, receivers & 3 new & 2 new, 3 modified & calendar, faults \\
  \hline
  Mid-value selection             & receivers & 4 new, 3 modified & 2 modified & ASM, voting \\
  \hline
  \end{tabular}
  \caption{Refactoring effort for protocol modifications, measured by which portions of the model have to be modified.}
  \label{fig:effort}
\end{figure}

@@

\paragraph{Omissive asymmetric faults.}
Removing faults already described by the fault model is easy. Recall that in our model faults do not appear in the system specification and only operate on the calendar. Removing a fault from the system requires only setting the number of a particular kind of faults to zero in the maximum fault assumption.

@@

\paragraph{Mid-value selection.}
Our $\OMH(1)$ model leverages majority vote in order to tolerate faults. Another choice for the fault masking algorithm used here is mid-value select (or median). This choice is more common in applications involving hardware, signal selection (where signal values cannot be relied on to exactly match even in the absence of faults), or cases where information about congruence is useful. To implement mid-value select in our model, we allow messages sent to take values in $\mathbb{R}$ and the receiver transition system is modified in two ways. First, a second buffer is introduced which will hold the sorted contents of the main buffer once voting has commenced. Second, a mid-value select function is called on the sorted buffer and the result is stored as the receiver's vote. The only invariants needing modification were the ASM definition (to account for the values stored by the new buffer and the relation between it and the main buffer) and the voting invariant.
